Population Differentiation Analysis

### 2017-11-10 doc/RMD/pop-diff.Rmd
add colon after source

```{r dapc-region-prob, fig.width = 7, fig.height = 6}
region_summary <- region.dapc$posterior %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  add_column(Individual = indNames(dat11cc)) %>% 
  add_column(`Original Population` = as.character(strata(dat11cc)$Region)) %>% 
  group_by(`Original Population`) %>%
  mutate(n = n()) %>%
  gather(Population, Posterior, -Individual, -`Original Population`, -n) %>% 
  group_by(Population, `Original Population`, n) %>% 
  summarize(`Mean Assignment` = mean(Posterior)) %>% 
  arrange(`Mean Assignment`) %>% 
  mutate(Source = case_when(
    Population == `Original Population` ~ "Original Population",
    TRUE ~ "Other"
    )) %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  mutate(`Original Population` = forcats::fct_inorder(`Original Population`)) %>%
  mutate(Population = factor(Population, levels(`Original Population`))) %>%
  mutate(`Original Population` = paste0(`Original Population`, " (", n, ")")) %>%
  mutate(`Original Population` = forcats::fct_inorder(`Original Population`))
REGION_PLOT <- region_summary %>%
  filter(n >= 10) %>%
  ggplot(aes(x = Population, y = `Mean Assignment`)) +
  geom_segment(aes(xend = Population, yend = 0)) +
  geom_point(aes(fill = Source), pch = 21, size = 2) + 
  facet_wrap(~`Original Population`, ncol = 3, strip.position = "top") +
  scale_fill_grey() +
  # scale_x_discrete(position = "top") +
  scale_y_continuous(limits = c(0, 1), minor_breaks = c(seq(0, 1, by = 0.125)), breaks = c(0, 0.5, 1), position = "right") +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "top") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  theme(axis.ticks.y = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  # theme(axis.text.x.top = element_text(angle = 90, vjust = 0.5, hjust = 0)) +
  theme(panel.grid.major.x = element_line(linetype = 0, color = "grey50")) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(linetype = 3, colour = "grey50")) +
  # theme(panel.spacing.y = unit(0, "line")) +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank()) +
  xlab("Population Assignment") +
  ylab("Mean Probability")
REGION_PLOT

>>>>

```{r dapc-region-prob, fig.width = 7, fig.height = 6}
region_summary <- region.dapc$posterior %>% 
  as.data.frame() %>% 
  as_tibble() %>% 
  add_column(Individual = indNames(dat11cc)) %>% 
  add_column(`Original Population` = as.character(strata(dat11cc)$Region)) %>% 
  group_by(`Original Population`) %>%
  mutate(n = n()) %>%
  gather(Population, Posterior, -Individual, -`Original Population`, -n) %>% 
  group_by(Population, `Original Population`, n) %>% 
  summarize(`Mean Assignment` = mean(Posterior)) %>% 
  arrange(`Mean Assignment`) %>% 
  mutate(Source = case_when(
    Population == `Original Population` ~ "Original Population",
    TRUE ~ "Other"
    )) %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  mutate(`Original Population` = forcats::fct_inorder(`Original Population`)) %>%
  mutate(Population = factor(Population, levels(`Original Population`))) %>%
  mutate(`Original Population` = paste0(`Original Population`, " (", n, ")")) %>%
  mutate(`Original Population` = forcats::fct_inorder(`Original Population`))
REGION_PLOT <- region_summary %>%
  filter(n >= 10) %>%
  ggplot(aes(x = Population, y = `Mean Assignment`)) +
  geom_segment(aes(xend = Population, yend = 0)) +
  geom_point(aes(fill = Source), pch = 21, size = 2) + 
  facet_wrap(~`Original Population`, ncol = 3, strip.position = "top") +
  scale_fill_grey() +
  # scale_x_discrete(position = "top") +
  scale_y_continuous(limits = c(0, 1), minor_breaks = c(seq(0, 1, by = 0.125)), breaks = c(0, 0.5, 1), position = "right") +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(legend.position = "top") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  theme(axis.ticks.y = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  # theme(axis.text.x.top = element_text(angle = 90, vjust = 0.5, hjust = 0)) +
  theme(panel.grid.major.x = element_line(linetype = 0, color = "grey50")) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(linetype = 3, colour = "grey50")) +
  # theme(panel.spacing.y = unit(0, "line")) +
  theme(strip.background = element_rect(color = NA, fill = "grey90")) +
  theme(strip.text = element_text(face = "bold", hjust = 0.05)) +
  theme(panel.border = element_blank()) +
  xlab("Population Assignment") +
  ylab("Mean Probability") +
  labs(list(fill = "Source:"))
REGION_PLOT
